\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-07 paper.qmd
Updated Figure 12

```{r}
#| fig-height: 5
#| fig-width: 15
#| fig-pos: H
generate_error_plots_one_c_shaped()
```

>>>>

```{r}
#| label: fig-one-dens_clust-error
#| fig-height: 3
#| fig-width: 9
#| fig-pos: H
#| fig-cap: "All \\gD{} layouts show high error in the sparse end. Three \\gD{} layouts: (a) tSNE, (b) UMAP, (c) PaCMaP of C-shaped densed cluster coloured by high-dimensional absolute error. Darker color shows high error while light colors shows low errors. Irrespective of the NLDR method, dense end of the structure shows the low error while sparse end of the structure shows the high error, because."
generate_error_plots_one_c_shaped()
```

### 2025-01-07 paper.tex
Initial work on the effect of density
Updated Figure 12

>>>>

\includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/fig-one-dens_clust-error-1.pdf}

\caption{\label{fig-one-dens_clust-error}All \gD{} layouts show high
error in the sparse end. Three \gD{} layouts: (a) tSNE, (b) UMAP, (c)
PaCMaP of C-shaped densed cluster coloured by high-dimensional absolute
error. Darker color shows high error while light colors shows low
errors. Irrespective of the NLDR method, dense end of the structure
shows the low error while sparse end of the structure shows the high
error, because.}
